Confinement induced resonance

### 2015-05-15 term-paper/paper.tex
[term-paper] 3.3

\subsection{Bound state in one dimension}

>>>>

\subsection{Bound state in one dimension}
In the case of a one dimentional system, $d_\perp=2$. Let $\varepsilon=\dfrac{E}{\omega}-1$, which is the energy of the system above the zero point energy of the confinement. For low energy state (i.e. $\abs{\varepsilon}\ll1$)
\eqar{
  T^{-1}\approx&\frac{m}{4\pi a}+\frac{m}{4\pi}\sqrt{\frac{m\omega}{2}}\paren{\sqrt{\frac{2}{-\varepsilon}}+O\paren{1}}
}
The pole of the $T$-matrix gives the energy of the bound state and we can see that the energy for the bound states is given by
\eqar{
  \varepsilon=-m\omega^2a^2
}
Compare to the case of a free space Feshbach resonance which only have bound states for a positive scattering length, a bound state exist even for negetive scattering length when the system is confined in one dimension.
